### 2018-01-03 derivations.tex
use custom macros to make life easy

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[
    backend=biber,
    style=numeric,
    citestyle=numeric,
    sorting=none
]{biblatex}
\addbibresource{derivations.bib}
% dcases
\usepackage{mathtools}
% for text right arrow
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[breaklinks=true, linkcolor=blue, citecolor=blue, colorlinks=true]{hyperref}
% load after hyperref
\usepackage[english,capitalise]{cleveref}

\newcommand{\pluseq}{\mathrel{{+}{=}}}
\newcommand{\minuseq}{\mathrel{{-}{=}}}
\newcommand{\ns}{\ensuremath{{N_{sp}}}}
\newcommand{\nr}{\ensuremath{{N_{reac}}}}
\newcommand{\conp}{CONP}
\newcommand{\conv}{CONV}
\newcommand{\dconp}{\ensuremath{,\qquad\text{for \conp}}}
\newcommand{\dconv}{\ensuremath{,\qquad\text{for \conv}}}
\newcommand{\Ru}{\ensuremath{\mathcal{R}}}

@@

For a reaction enhanced (or diminished) by the presence of a third body, the reaction rate is modified by the third-body concentration $[X]_i$ given by
\begin{equation}
[X]_{i} = \sum_{k=1}^{\ns} \alpha_{k,i} [C]_{k} \;,
\end{equation}
where $\alpha_{k,i}$ is the third-body efficiency of species $k$ in the $i$th reaction.
For a default third-body efficiency of $\alpha_{k,i} = 1$, this may be rearranged to the compact-storage form:
\begin{equation}
 [X]_{i} = [C] + \sum_{k=1}^{\ns} \left(\alpha_{k,i} - 1\right) [C]_{k} \;,
\end{equation}
where only species with non-default third-body efficiencies must be stored in the model.
Expanding the concentration of the last species gives:
\begin{equation}
\label{e:thd_mix}
 [X]_{i}=[C] \alpha_{\ns,i} + \sum_{k=1}^{-1 + \ns} \left(- \alpha_{\ns,i} + \alpha_{k,i}\right) [C]_{k}\;.
\end{equation}
If all species in the mixture contribute equally as third bodies, then $\alpha_{k,i} = 1$ for all species:
\begin{equation}
\label{e:thd_unity}
 [X]_{i} = [C] = \frac{P}{\Ru T} \;.
\end{equation}
In addition, a single species may act as the third body in which case
\begin{equation}
 [X]_{i} = [C_m]
\end{equation}
where the $m$th species is the third body.
For evaluation of Jacobian entries, the expanded form:
\begin{equation}
\label{e:thd_spec}
 [X]_{i}=\left([C] - \sum_{k=1}^{-1 + \ns} [C]_{k}\right) \delta_{\ns m} + \left(- \delta_{\ns m} + 1\right) [C]_{m}
\end{equation}
will be used, where the Kronecker delta $\delta_{\ns m}$ is unity if and only if the third body species $m$ is the last species in the model.

\subsection{Falloff reactions}
Unlike elementary and third-body reactions, falloff reactions exhibit a pressure dependence described as a blending of rates at low- and high-pressure limits; thus, the rate coefficients depend on a mixture of low-pressure- ($k_{0, i}$) and high-pressure-limit ($k_{\infty,i}$) coefficients, each with corresponding Arrhenius parameters and expressed using Eq.~\cref{e:arrhenius}.
The ratio of the coefficients $k_{0, i}$ and $k_{\infty, i}$, combined with the third-body concentration (based on either the mixture as a whole including any efficiencies $\alpha_{k,i}$, or a specific species), define a reduced pressure $P_{r,i}$ given by
\begin{equation}
 P_{r, i}=\frac{[X]_{i} k_{0, i}}{k_{\infty, i}}
\end{equation}
where $[X]_{i}$ is the appropriate third-body concentration as described in~\cref{s:thdbody}

@@

Following the outline of~\cref{s:rop_molar}, the forward rate of progress derivatives are:
\begin{subequations}
 \begin{align}
  \frac{\partial {R_f} }{\partial V }_{i} &= \frac{[C] S^{\prime}_{\ns}}{V} {k_f}_{i} - \frac{{R_f}_{i}}{V} \sum_{k=1}^{\ns} \nu^{\prime}_{k,i}&\dconp\\
  \frac{\partial {R_f} }{\partial P }_{i} &= \frac{S^{\prime}_{\ns} {k_f}_{i}}{T \Ru}&\dconv
 \end{align}
\end{subequations}
and similarly, the reverse rate of progress derivatives:
\begin{subequations}
 \begin{align}
  \frac{\partial {R_r} }{\partial V }_{i} &= \frac{[C] S^{\prime\prime}_{\ns}}{V} {k_r}_{i} - \frac{{R_r}_{i}}{V} \sum_{k=1}^{\ns} \nu^{\prime\prime}_{k,i}&\dconp\\
  \frac{\partial {R_r} }{\partial P }_{i} &= \frac{S^{\prime\prime}_{\ns} {k_r}_{i}}{T \Ru}&\dconv
 \end{align}
\end{subequations}
giving finally:
\begin{subequations}
 \label{e:dropi_de}
 % linebreak and parenthesis sizing:
 % https://tex.stackexchange.com/questions/49890/linebreak-between-left-and-right/49895
 \begin{align}
  \frac{\partial {R} }{\partial V }_{i} &= \frac{1}{V}\left(\vphantom{{R_r}_{i} \sum_{k=1}^{\ns} \nu^{\prime\prime}_{k,i}} [C]\left(S^{\prime}_{\ns} {k_f}_{i} - S^{\prime\prime}_{\ns} {k_r}_{i}\right) + \right.& \nonumber\\
  &\left. \quad\left({R_r}_{i} \sum_{k=1}^{\ns} \nu^{\prime\prime}_{k,i} - {R_f}_{i} \sum_{k=1}^{\ns} \nu^{\prime}_{k,i}\right) \right)&\dconp\\
  \frac{\partial {R} }{\partial P }_{i} &= \frac{1}{T \Ru} \left(S^{\prime}_{\ns} {k_f}_{i} - S^{\prime\prime}_{\ns} {k_r}_{i}\right)&\dconv
 \end{align}
\end{subequations}

\subsection{Pressure modification\slash Falloff function derivatives}

>>>>

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[
    backend=biber,
    style=numeric,
    citestyle=numeric,
    sorting=none
]{biblatex}
\addbibresource{derivations.bib}

% dcases
\usepackage{mathtools}
% for text right arrow
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{amsmath,eqparbox,xparse}
\usepackage[breaklinks=true, linkcolor=blue, citecolor=blue, colorlinks=true]{hyperref}
% load after hyperref
\usepackage[english,capitalise]{cleveref}

% https://tex.stackexchange.com/a/34412/5764
\makeatletter
\NewDocumentCommand{\eqmathbox}{o O{c} m}{%
  \IfValueTF{#1}
    {\def\eqmathbox@##1##2{\eqmakebox[#1][#2]{$##1##2$}}}
    {\def\eqmathbox@##1##2{\eqmakebox{$##1##2$}}}
  \mathpalette\eqmathbox@{#3}
}
\makeatother

\newcommand{\pluseq}{\mathrel{{+}{=}}}
\newcommand{\minuseq}{\mathrel{{-}{=}}}
\newcommand{\ns}{N_{sp}}
\newcommand{\nr}{N_{reac}}
\newcommand{\conp}{CONP}
\newcommand{\conv}{CONV}
\newcommand{\dconp}{\ifmmode\text{for \conp,}\else for \conp,\fi}
\newcommand{\dconv}{\ifmmode\text{for \conv,}\else for \conv,\fi}
\newcommand{\Ru}{\mathcal{R}}

% simple command for equal-sized eqmathbox's on the lhs / rhs and conditional
% arguements are tag, text, alignment
\NewDocumentCommand{\lhs}{mmO{r}}{\eqmathbox[LHS_#1][#3]{#2}}
\NewDocumentCommand{\rhs}{mmO{l}}{\eqmathbox[RHS_#1][#3]{#2}}
\NewDocumentCommand{\cond}{mmO{r}}{\eqmakebox[COND_#1][#3]{#2}}

% treat subequations as equation for cleverref
% https://tex.stackexchange.com/a/308627/56227
\crefalias{subequation}{equation}

@@

For a reaction enhanced (or diminished) by the presence of a third body, the reaction rate is modified by the third-body concentration $[X]_i$ given by
\begin{equation}
[X]_{i} = \sum_{k=1}^{\ns} \alpha_{k,i} [C]_{k} \;,
\end{equation}
where $\alpha_{k,i}$ is the third-body efficiency of species $k$ in the $i$th reaction.
For a default third-body efficiency of $\alpha_{k,i} = 1$, this may be rearranged to the compact-storage form:
\begin{equation}
 [X]_{i} = [C] + \sum_{k=1}^{\ns} \left(\alpha_{k,i} - 1\right) [C]_{k} \;,
\end{equation}
where only species with non-default third-body efficiencies must be stored in the model.
Expanding the concentration of the last species gives:
\begin{equation}
\label{e:thd_mix}
 [X]_{i}=[C] \alpha_{\ns,i} + \sum_{k=1}^{-1 + \ns} \left(- \alpha_{\ns,i} + \alpha_{k,i}\right) [C]_{k}\;.
\end{equation}
This form will be denoted as the \textbf{mixture}-based third-body efficiency.

If all species in the mixture contribute equally as third bodies, then $\alpha_{k,i} = 1$ for all species:
\begin{equation}
\label{e:thd_unity}
 [X]_{i} = [C] = \frac{P}{\Ru T} \;.
\end{equation}
This form will be called the \textbf{unity}-based third-body efficiency.

In addition, a single species may act as the third body in which case
\begin{equation}
 [X]_{i} = [C_m]
\end{equation}
where the $m$th species is the third body.
For evaluation of Jacobian entries, the expanded form:
\begin{equation}
\label{e:thd_spec}
 [X]_{i}=\left([C] - \sum_{k=1}^{-1 + \ns} [C]_{k}\right) \delta_{\ns m} + \left(- \delta_{\ns m} + 1\right) [C]_{m}
\end{equation}
will be used, where the Kronecker delta $\delta_{\ns m}$ is unity if and only if the third body species $m$ is the last species in the model.
\Cref{e:thd_spec} will be referred to as the \textbf{species}-based third-body efficiency.

\subsection{Falloff reactions}
Unlike elementary and third-body reactions, falloff reactions exhibit a pressure dependence described as a blending of rates at low- and high-pressure limits; thus, the rate coefficients depend on a mixture of low-pressure- ($k_{0, i}$) and high-pressure-limit ($k_{\infty,i}$) coefficients, each with corresponding Arrhenius parameters and expressed using Eq.~\cref{e:arrhenius}.
The ratio of the coefficients $k_{0, i}$ and $k_{\infty, i}$, combined with the third-body concentration (based on either the mixture as a whole including any efficiencies $\alpha_{k,i}$, or a specific species), define a reduced pressure $P_{r,i}$ given by
\begin{equation}
 \label{e:pr}
 P_{r, i}=\frac{[X]_{i} k_{0, i}}{k_{\infty, i}}
\end{equation}
where $[X]_{i}$ is the appropriate third-body concentration as described in~\cref{s:thdbody}

@@

Following the outline of~\cref{s:rop_molar}, the forward rate of progress derivatives are:
\begin{subequations}
 \begin{align}
  \frac{\partial {R_f}_{i} }{\partial V } &= \frac{[C] S^{\prime}_{\ns}}{V} {k_f}_{i} - \frac{{R_f}_{i}}{V} \sum_{k=1}^{\ns} \nu^{\prime}_{k,i}&\dconp\\
  \frac{\partial {R_f}_{i} }{\partial P } &= \frac{S^{\prime}_{\ns} {k_f}_{i}}{T \Ru}&\dconv
 \end{align}
\end{subequations}
and similarly, the reverse rate of progress derivatives:
\begin{subequations}
 \begin{align}
  \frac{\partial {R_r}_{i} }{\partial V } &= \frac{[C] S^{\prime\prime}_{\ns}}{V} {k_r}_{i} - \frac{{R_r}_{i}}{V} \sum_{k=1}^{\ns} \nu^{\prime\prime}_{k,i}&\dconp\\
  \frac{\partial {R_r}_{i} }{\partial P } &= \frac{S^{\prime\prime}_{\ns} {k_r}_{i}}{T \Ru}&\dconv
 \end{align}
\end{subequations}
giving finally:
\begin{subequations}
 \label{e:dropi_de}
 % linebreak and parenthesis sizing:
 % https://tex.stackexchange.com/questions/49890/linebreak-between-left-and-right/49895
 \begin{align}
  \frac{\partial {R}_{i} }{\partial V } &= \frac{1}{V}\left(\vphantom{{R_r}_{i} \sum_{k=1}^{\ns} \nu^{\prime\prime}_{k,i}} [C]\left(S^{\prime}_{\ns} {k_f}_{i} - S^{\prime\prime}_{\ns} {k_r}_{i}\right) + \right.& \nonumber\\
  &\left. \quad\left({R_r}_{i} \sum_{k=1}^{\ns} \nu^{\prime\prime}_{k,i} - {R_f}_{i} \sum_{k=1}^{\ns} \nu^{\prime}_{k,i}\right) \right)&\dconp\\
  \frac{\partial {R}_{i} }{\partial P } &= \frac{1}{T \Ru} \left(S^{\prime}_{\ns} {k_f}_{i} - S^{\prime\prime}_{\ns} {k_r}_{i}\right)&\dconv
 \end{align}
\end{subequations}

\subsection{Pressure modification\slash Falloff function derivatives}
\subsubsection{Elementary reactions}
For elementary reactions, all derivatives of the pressure-modification term are zero:
\begin{align}
\lhs{dci_elem}{\frac{\partial c_{i} }{\partial T }} &= \rhs{dci_elem}{0} & \cond{dci_elem}{,} \label{e:dci_elem_dt} \\
\lhs{dci_elem}{\frac{\partial c_{i} }{\partial {n_j} }} &= \rhs{dci_elem}{0} & \cond{dci_elem}{,} \label{e:dci_elem_dnj} \\
\end{align}
and:
\begin{subequations}
 \label{e:dci_elem_de}
 \begin{align}
  \lhs{dci_elem}{\frac{\partial c_{i} }{\partial V }} &= \rhs{dci_elem}{0} & \cond{dci_elem}{\dconp} \\
  \lhs{dci_elem}{\frac{\partial c_{i} }{\partial P }} &= \rhs{dci_elem}{0} & \cond{dci_elem}{\dconv}
 \end{align}
\end{subequations}

\subsubsection{Third-body enhanced reactions}
For a third-body enhanced reaction~\cref{e:thd_mix} is differentiated to give:
\begin{align}
 \lhs{dci_thd_mix}{\frac{\partial [X]_i }{\partial T }} &= \rhs{dci_thd_mix}{-\frac{[C] \alpha_{\ns,i}}{T}} & \cond{dci_thd_mix}{,} \label{e:dci_thd_dt} \\
 \lhs{dci_thd_mix}{\frac{\partial [X]_i }{\partial n_{j}}} &= \rhs{dci_thd_mix}{\frac{1}{V} \left(- \alpha_{\ns,i} + \alpha_{j,i}\right)} & \cond{dci_thd_mix}{,} \label{e:dci_thd_dnj}
\end{align}
and:
\begin{subequations}
 \label{e:dci_thd_de}
 \begin{align}
  \lhs{dci_thd_mix}{\frac{\partial [X]_i }{\partial V }} &= \rhs{dci_thd_mix}{\frac{1}{V} \left([C] \alpha_{\ns,i} - [X]_{i}\right)} & \cond{dci_thd_mix}{\dconp}\\
  \lhs{dci_thd_mix}{\frac{\partial [X]_i }{\partial P }} &= \rhs{dci_thd_mix}{\frac{\alpha_{\ns,i}}{T \Ru}} & \cond{dci_thd_mix}{\dconv}
 \end{align}
\end{subequations}

If $\alpha_{j,i} = 1$ for all species $j$,~\cref{e:dci_thd_dt,e:dci_thd_dnj,e:dci_thd_de} may be simplified to:
\begin{align}
 \lhs{dci_thd_unity}{\frac{\partial c_{i} }{\partial T }} &= \rhs{dci_thd_unity}{- \frac{[C]}{T}}& \cond{dci_thd_unity}{,} \label{e:dci_thd_unity_dt} \\
 \lhs{dci_thd_unity}{\frac{\partial c_{i} }{\partial n_{j} }} &= \rhs{dci_thd_unity}{0}& \cond{dci_thd_unity}{,}
\end{align}
and:
\begin{subequations}
 \label{e:dci_thd_unity_de}
 \begin{align}
  \lhs{dci_thd_unity}{\frac{\partial c_{i} }{\partial V }} &= \rhs{dci_thd_unity}{0} & \cond{dci_thd_unity}{\dconp} \\
  \lhs{dci_thd_unity}{\frac{\partial c_{i} }{\partial P }} &= \rhs{dci_thd_unity}{\frac{1}{T \Ru}}& \cond{dci_thd_unity}{\dconv}
 \end{align}
\end{subequations}

If the third-body is the $m$th species,~\cref{e:dci_thd_dt,e:dci_thd_dnj,e:dci_thd_de} become:
\begin{align}
 \lhs{dci_thd_spec}{\frac{\partial c_{i} }{\partial T }} &= \rhs{dci_thd_spec}{-\frac{\delta_{\ns m}}{T} [C]}&\cond{dci_thd_spec}{,} \label{e:dci_thd_spec_dt} \\
 \lhs{dci_thd_spec}{\frac{\partial c_{i} }{\partial n_j }} &= \rhs{dci_thd_spec}{\frac{1}{V} \left(- \delta_{\ns m} + \delta_{j m}\right)}&\cond{dci_thd_spec}{,} \label{e:dci_thd_spec_dnj} \\
\end{align}
and:
\begin{subequations}
\label{e:dci_thd_spec_de}
\begin{align}
\lhs{dci_thd_spec}{\frac{\partial c_{i} }{\partial V }} &= \rhs{dci_thd_spec}{\frac{\delta_{\ns m}}{V} \left([C] - [C]_{\ns}\right) + \frac{[C]_{m}}{V} \left(\delta_{\ns m} - 1\right)} & \cond{dci_thd_spec}{\dconp} \\
\lhs{dci_thd_spec}{\frac{\partial c_{i} }{\partial P }} &= \rhs{dci_thd_spec}{\frac{\delta_{\ns m}}{T \Ru}} & \cond{dci_thd_spec}{\dconv}
\end{align}
\end{subequations}

\subsubsection{Unimolecular\slash~recombination fall-off reactions}
\label{s:dfall}
Derivatives of the third-body pressure modification term for unimolecular\slash~recombination fall-off reactions---given by~\cref{e:rxn_pressure}---are quite involved, and will be broken up over the next sections.
The derivative of full third-body pressure modification term for fall-off reactions will be given in this section, while~\cref{s:dchem} will provide the same derivatives for chemically-activated bimolecular reactions.
Subsequently, the derivatives of the reduced pressure and falloff blending factors will be explored in~\cref{s:dpr,s:dfi} respectively.

The derivatives of the unimolecular\slash~recombination fall-off reaction third-body pressure modification term are:
\begin{align}
 \lhs{dci_fall}{\frac{\partial c_{i} }{\partial T }} &= \rhs{dci_fall}{\frac{1}{P_{r, i} + 1} \left(P_{r, i} \frac{\partial F_{i} }{\partial T } + \frac{\partial P_{r, i} }{\partial T } \left(F_{i} - c_{i}\right)\right)} & \cond{dci_fall}{,} \label{e:dci_fall_dt}\\
 \lhs{dci_fall}{\frac{\partial c_{i} }{\partial n_j}} &= \rhs{dci_fall}{\frac{1}{P_{r, i} + 1} \left(P_{r, i} \frac{\partial F_{i} }{\partial n[j] } + \frac{\partial P_{r, i} }{\partial n_j } \left(F_{i} - c_{i}\right)\right)} & \cond{dci_fall}{,} \label{e:dci_fall_dnj}
\end{align}
and with respect to the thermodynamic parameter:
\begin{subequations}
 \label{e:dci_fall_de}
 \begin{align}
  \lhs{dci_fall}{\frac{\partial c_i }{\partial V }} &= \rhs{dci_fall}{\frac{1}{P_{r, i} + 1} \left(P_{r, i} \frac{\partial F_{i} }{\partial V } + \frac{\partial P_{r, i} }{\partial V } \left(F_{i} - c_{i}\right)\right)} & \cond{dci_fall}{\dconp} \\
  \lhs{dci_fall}{\frac{\partial c_i }{\partial P }} &= \rhs{dci_fall}{\frac{1}{P_{r, i} + 1} \left(P_{r, i} \frac{\partial F_{i} }{\partial P } + \frac{\partial P_{r, i} }{\partial P } \left(F_{i} - c_{i}\right)\right)} & \cond{dci_fall}{\dconv}
 \end{align}
\end{subequations}

\subsubsection{Chemically-activated bimolecular reactions}
\label{s:dchem}

Similarly, the chemically-activated bimolecular reactions are as follows:
\begin{align}
 \label{e:dci_chem_dt}
 \lhs{dci_chem}{\frac{\partial c_i }{\partial T }} &= \rhs{dci_chem}{\frac{1}{P_{r, i} + 1} \left(\frac{\partial F_{i} }{\partial T } - \frac{\partial P_{r, i} }{\partial T } c_{i}\right)} & \cond{dci_chem}{,} \\
 \label{e:dci_chem_dnj}
 \lhs{dci_chem}{\frac{\partial c_i }{\partial n_j }} &= \rhs{dci_chem}{\frac{1}{P_{r, i} + 1} \left(\frac{\partial F_{i} }{\partial n_j } - \frac{\partial P_{r, i} }{\partial n_j } c_{i}\right)} & \cond{dci_chem}{,}
\end{align}
and:
\begin{subequations}
 \label{e:dci_chem_de}
 \begin{align}
  \lhs{dci_chem}{\frac{\partial c_i }{\partial V }} &= \rhs{dci_chem}{\frac{1}{P_{r, i} + 1} \left(\frac{\partial F_{i} }{\partial V } - \frac{\partial P_{r, i} }{\partial V } c_{i}\right)} & \cond{dci_chem}{\dconp} \\
  \lhs{dci_chem}{\frac{\partial c_i }{\partial P }} &= \rhs{dci_chem}{\frac{1}{P_{r, i} + 1} \left(\frac{\partial F_{i} }{\partial P } - \frac{\partial P_{r, i} }{\partial P } c_{i}\right)} & \cond{dci_chem}{\dconv}
 \end{align}
\end{subequations}

\subsubsection{Reduced pressure}
\label{s:dpr}

Next the reduced pressure derivatives in~\crefrange{e:dci_fall_dt}{e:dci_chem_de} will be evaluated; these depend on the form of the third-body efficiency used in~\cref{e:pr}, thus we will first work out the derivatives for each third-body efficiency form, and then develop a generalized form for compact representation.
For a third-body concentration based upon the entire mixture, (i.e.,~\cref{e:thd_mix}) the derivatives are:
\begin{align}
 \lhs{dpr_mix}{\frac{\partial P_{r, i} }{\partial T }} &= \rhs{dpr_mix}{\frac{P_{r, i}}{T} \left(\beta_{0} - \beta_{\infty} + \frac{E_{a, 0}}{T \Ru} - \frac{E_{a, \infty}}{T \Ru}\right) - \frac{[C] k_{0, i} \alpha_{\ns,i}}{T k_{\infty, i}}} & {,} \label{e:dpr_mix_dt} \\
 \lhs{dpr_mix}{\frac{\partial P_{r, i} }{\partial n_j }} &= \rhs{dpr_mix}{\frac{k_{0, i} \left(- \alpha_{\ns,i} + \alpha_{j,i}\right)}{k_{\infty, i} V}} & \cond{dpr_mix}{,} \label{e:dpr_mix_dnj}
\end{align}
and:
\begin{subequations}
 \label{e:dpr_mix_de}
 \begin{align}
  \lhs{dpr_mix}{\frac{\partial P_{r, i} }{\partial V }} &= \rhs{dpr_mix}{- \frac{P_{r, i}}{V} + \frac{[C] k_{0, i} \alpha_{\ns,i}}{V k_{\infty, i}}} & \cond{dpr_mix}{\dconp} \\
  \lhs{dpr_mix}{\frac{\partial P_{r, i} }{\partial P }} &= \rhs{dpr_mix}{\frac{k_{0, i} \alpha_{\ns,i}}{T k_{\infty, i} \Ru}} & \cond{dpr_mix}{\dconv}
 \end{align}
\end{subequations}

For a unity third-body concentration (i.e., all $\alpha_{k,i}=1$):
\begin{align}
 \lhs{dpr_unity}{\frac{\partial P_{r, i} }{\partial T }} &= \rhs{dpr_unity}{\frac{P_{r, i}}{T} \left(\beta_{0} - \beta_{\infty} - 1 + \frac{E_{a, 0}}{T \Ru} - \frac{E_{a, \infty}}{T \Ru}\right)} & \cond{dpr_unity}{,} \label{e:dpr_unity_dt} \\
 \lhs{dpr_unity}{\frac{\partial P_{r, i} }{\partial n_j }} &= \rhs{dpr_unity}{0} & \cond{dpr_unity}{,} \label{e:dpr_unity_dnj}
\end{align}
and:
\begin{subequations}
 \label{e:dpr_unity_de}
 \begin{align}
  \lhs{dpr_unity}{\frac{\partial P_{r, i} }{\partial V }} &= \rhs{dpr_unity}{0} & \cond{dpr_unity}{\dconp}\\
  \lhs{dpr_unity}{\frac{\partial P_{r, i} }{\partial P }} &= \rhs{dpr_unity}{\frac{k_{0, i}}{k_{\infty, i}} \frac{1}{\Ru T}} & \cond{dpr_unity}{\dconv}
 \end{align}
\end{subequations}

Finally, for species-based third-body (i.e., the species $m$ alone acts as the third body):
\begin{align}
 \lhs{dpr_spec}{\frac{\partial P_{r, i} }{\partial T }} &=\rhs{dpr_spec}{\frac{P_{r, i}}{T} \left(\beta_{0} - \beta_{\infty} + \frac{E_{a, 0}}{T \Ru} - \frac{E_{a, \infty}}{T \Ru}\right) - \frac{[C] k_{0, i} \delta_{\ns m}}{T k_{\infty, i}}} & \cond{dpr_spec}{,} \label{e:dpr_spec_dt} \\
 \lhs{dpr_spec}{\frac{\partial P_{r, i} }{\partial n_j }} &=\rhs{dpr_spec}{\frac{k_{0, i}}{V k_{\infty, i}} \left(- \delta_{\ns m} + \delta_{j m}\right)} & \cond{dpr_spec}{,} \label{e:dpr_spec_dnj}
\end{align}
and:
\begin{subequations}
 \label{e:dpr_spec_de}
 \begin{align}
  \lhs{dpr_spec}{\frac{\partial P_{r, i} }{\partial V }} &= \rhs{dpr_spec}{- \frac{P_{r, i}}{V} + \frac{[C] k_{0, i} \delta_{\ns m}}{V k_{\infty, i}}} & \cond{dpr_spec}{\dconp}\\
  \lhs{dpr_spec}{\frac{\partial P_{r, i} }{\partial P }} &= \rhs{dpr_spec}{\frac{k_{0, i} \delta_{\ns m}}{T k_{\infty, i} \Ru}} & \cond{dpr_spec}{\dconv}
 \end{align}
\end{subequations}

\Crefrange{e:dpr_mix_dt}{e:dpr_spec_de} may be recast in a more generalized form using temporary variables $\Theta_{\partial P_{r, i}, \ldots}$ and $\bar{\theta}_{\partial P_{r, i}, \ldots}$ to replace terms in the derivative:
\begin{align}
 \lhs{dpr_gen}{\frac{\partial P_{r, i} }{\partial T } } &= \rhs{dpr_gen}{P_{r, i} \Theta_{P_{r,i}, \partial T} + \bar{\theta}_{P_{r, i}, \partial T}} & \cond{dpr_gen}{,} \label{e:dpr_dt} \\
 \lhs{dpr_gen}{\frac{\partial P_{r, i} }{\partial n_j}} &= \rhs{dpr_gen}{\frac{\bar{\theta}_{P_{r, i}, \partial n_j}}{V k_{\infty, i}} k_{0, i}} & \cond{dpr_gen}{,} \label{e:dpr_dnj}
\end{align}
and:
\begin{subequations}
 \label{e:dpr_de}
 \begin{align}
  \lhs{dpr_gen}{\frac{\partial P_{r, i} }{\partial V}} &= \rhs{dpr_gen}{P_{r, i} \Theta_{P_{r,i}, \partial V} + \bar{\theta}_{P_{r, i}, \partial V}} & \cond{dpr_gen}{\dconp} \\
  \lhs{dpr_gen}{\frac{\partial P_{r, i} }{\partial P}} &= \rhs{dpr_gen}{\bar{\theta}_{P_{r, i}, \partial P}} & \cond{dpr_gen}{\dconv}
 \end{align}
\end{subequations}
with:
\begin{align}
 \label{e:dpr_theta}
 \Theta_{P_{r,i}, \partial T} &=
 \begin{dcases}
  \frac{1}{T} \left(\beta_{0} - \beta_{\infty} + \frac{E_{a, 0}}{T \Ru} - \frac{E_{a, \infty}}{T \Ru}\right) & \text{if mix,} \\
  \frac{1}{T} \left(\beta_{0} - \beta_{\infty} - 1 + \frac{E_{a, 0}}{T \Ru} - \frac{E_{a, \infty}}{T \Ru}\right) & \text{if unity,} \\
  \frac{1}{T} \left(\beta_{0} - \beta_{\infty} + \frac{E_{a, 0}}{T \Ru} - \frac{E_{a, \infty}}{T \Ru}\right) & \text{if species,}
 \end{dcases} \\
 \bar{\theta}_{P_{r, i}, \partial T} &=
 \begin{dcases}
  \rhs{theta_pr_bar_dt}{- \frac{[C] k_{0, i} \alpha_{\ns,i}}{T k_{\infty, i}}} & \text{if mix,} \\
  \rhs{theta_pr_bar_dt}{0}[c] & \text{if unity,} \\
  \rhs{theta_pr_bar_dt}{- \frac{[C] k_{0, i} \delta_{\ns m}}{T k_{\infty, i}}} & \text{if species,}
 \end{dcases} \\
 \bar{\theta}_{P_{r, i}, \partial n_j} &=
 \begin{dcases}
  \rhs{theta_pr_bar_dnj}{- \alpha_{\ns,i} + \alpha_{j,i}} & \text{if mix,} \\
  \rhs{theta_pr_bar_dnj}{0}[c] & \text{if unity,}  \\
  \rhs{theta_pr_bar_dnj}{- \delta_{\ns m} + \delta_{j m}} & \text{if species,}
 \end{dcases} \\
 \Theta_{P_{r,i}, \partial V} &=
 \begin{dcases}
  \rhs{Theta_pr_bar_dv}{- \frac{1}{V}} & \text{if mix,} \\
  \rhs{Theta_pr_bar_dv}{0}[c] & \text{if unity,}  \\
  \rhs{Theta_pr_bar_dv}{- \frac{1}{V}} & \text{if species,}
 \end{dcases} \\
 \bar{\theta}_{P_{r, i}, \partial V} &=
 \begin{dcases}
  \rhs{theta_pr_bar_dv}{\frac{[C] k_{0, i} \alpha_{\ns,i}}{V k_{\infty, i}}} & \text{if mix,} \\
  \rhs{theta_pr_bar_dv}{0}[c] & \text{if unity,}  \\
  \rhs{theta_pr_bar_dv}{\frac{[C] k_{0, i} \delta_{\ns m}}{V k_{\infty, i}}} & \text{if species,}
 \end{dcases} \\
 \bar{\theta}_{P_{r, i}, \partial P} &=
 \begin{dcases}
  \rhs{theta_pr_bar_dp}{\frac{k_{0, i} \alpha_{\ns,i}}{T k_{\infty, i} \Ru}} & \text{if mix,} \\
  \rhs{theta_pr_bar_dp}{\frac{k_{0, i}}{T k_{\infty, i} \Ru}} & \text{if unity,}  \\
  \rhs{theta_pr_bar_dp}{\frac{k_{0, i} \delta_{\ns m}}{T k_{\infty, i} \Ru}} & \text{if species,}
 \end{dcases} \\
\end{align}

\subsubsection{Falloff blending factor}
\label{s:dfi}

The falloff blending factor
